Predicting Fire Risk: \\ An Evaluation of the Fire Danger Index

### 2016-01-22 paper.tex

% !TeX spellcheck = <none>
\documentclass{article}
% Change Hons to PhD, MAE, MPhil or MComm as appropraite
% Remove singlespace and singleside for final version.

%\usepackage{lipsum}
\usepackage{float}
\usepackage{gensymb}
\usepackage{natbib}
\usepackage{pdfpages}
\usepackage{listings}
\title{Predicting Fire Risk: \\ An Evaluation of the Fire Danger Index}
\author{Elle Saber, Rob J Hyndman \& Di Cook}

@@

Regression splines are a method for modelling nonlinear data as a number of piecewise  polynomial functions. The points at which the functions join are called knots. For example when the functions join at $x=k$, $k$is known as a knot \citep{ruppert03}.

As a result the logistic model becomes
\begin{equation}
\label{eq logits}
\Pr(Y=1|X)=\frac{\exp(\sum_{k=1}^K f_k(x_k))}{1+\exp(\sum_{k=1}^K f_k(x_k)}
\end{equation}
where $Y$ denotes fire occurrence, $x_k$ denotes the $k^{th}$ predictor and each $f_k$ represents a penalized regression spline.

Regression splines can be subject to over fitting: where the fitted model adheres to the data too strongly and doesn't smooth out ~noise' enough. This results in great in-sample predictions but poor out-of-sample predictions. To prevent over fitting occurring we use an automated method that optimizes the number of knots by penalizing for non-smoothness; an overview of using penalized regression splines in this context is given by \citet{wood02}.

@@

\section*{Acknowledgment}
\textit{No one who achieves success does so without acknowledging the help of others. The wise and confident acknowledge this help with gratitude. -Alfred North Whitehead
	}

I am indebted to my indefatigable supervisors Rob and Di, thank you for your endless patience.

To those who I adopted as my pseudo-supervisors Souhaib Ben-Taieb, Klaus Ackerman, Simon Angus, your help and advice was invaluable.

To my biggest supporters Earo Wang \& Christien Blencowe without your encouragement, your help and Earo's endless of chocolate this year would have been impossible.

Special thanks to Sarah Harris (Earth \& Atmosphereic Science, Monash), Hamish Clarke (UNSW), Stuart Matthews (Rural Fire Service, NSW), Musa Kilinc \& Danielle Wright (Country Fire Authority), who all contributed with data and helpful advice.

To my long suffering honours cohort, I apologise for the tears and for boring you with my data struggles, you have been the the best team to be a part of.

% Appendices start here
\bibliographystyle{asa}

>>>>

% !TeX spellcheck = <none>
\documentclass[11pt,a4paper]{article}
% Change Hons to PhD, MAE, MPhil or MComm as appropraite
% Remove singlespace and singleside for final version.

\usepackage{float,fullpage}
\usepackage{gensymb}
\usepackage{natbib}
\usepackage{pdfpages}
\usepackage{listings}

\title{Predicting Fire Risk: \\ An Evaluation of the Fire Danger Index}
\author{Elle Saber, Rob J Hyndman \& Di Cook}

@@

Regression splines are a method for modelling nonlinear data as a number of piecewise  polynomial functions. The points at which the functions join are called knots. For example when the functions join at $x=k$, $k$ is known as a knot \citep{ruppert03}.

As a result the logistic model becomes
\begin{equation}
\label{eq logits}
\Pr(Y=1|X)=\frac{\exp(\sum_{k=1}^K f_k(x_k))}{1+\exp(\sum_{k=1}^K f_k(x_k)}
\end{equation}

where $Y$ denotes fire occurrence, $x_k$ denotes the $k^{th}$ predictor and each $f_k$ represents a penalized regression spline.

Regression splines can be subject to over fitting: where the fitted model adheres to the data too strongly and doesn't smooth out `noise' enough. This results in great in-sample predictions but poor out-of-sample predictions. To prevent over fitting occurring we use an automated method that optimizes the number of knots by penalizing for non-smoothness; an overview of using penalized regression splines in this context is given by \citet{wood02}.

@@

% Appendices start here
\bibliographystyle{agsm}
